\onecolumn
\section{ \LARGE Problems \& \\Solutions}

\subsection{} \IEEEPARstart{F}{irst} of all, \\
I had no idea about all of the terms in the Task.pdf,which really troubled me!
However,with my determination and ambition for new knowledge,I decided to get a general understanding of
these new terms firstly to have a overview of my following tasks.
Then I used search engine to accomplish above-mentioned things.
\newline
\subsection{TaskOne}~\newline
PB1:~ Before the kernel development, I prefered to have a rough command of \underline{CUDA} and programming on it 
through bilibili and csdn.\newline
~\newline~
PB2:~ However,when I decided to use the "nvprof" instruction,I finded out that it was \underline{replaced}
by some new tools NVIDIA Nsight Systems and NVIDIA Nsight Compute.~~
When I struggled to install and configure NVIDIA Nsight Systems and Compute, its all-English UI really troubled me.
So I have to learn how to use this tool to verify the availability of GPU computing power.\newline
It will take some time,but I am interested in it!\newline
Solution to PB2:~ When I read the help document of Nsys ,I was glad to find out that the instruction "nvprof"
could still use by using nsys nvprof!\newline
~\newline~
PB3:~ when I used the Nsight System to analyze the cuda program,it will always report an error when I use nsys-ui
which confused me a lot!!\newline
Solution to PB3:~ Through reading documents and referring information,I realized that error could be ignored 
which would not impact my analysis on Nsight!\newline
~\newline~
PB4 and Solution:~ optimizing the cuda kernel was so difficult which made me have to turn to AI and numerous videos 
to understand them step by step statement by statement.And I could not take a good command of them within a 
short days!\newline

\subsection{TaskTwo}~\newline
PB1 and Solution:~I haven't learn the proper nouns of operator performance, so I need to take a general 
comprehension of them.\newline
~\newline~
PB2:~ I couldn't find the TFLOPS data and some relevant data on Nsight Compute although I had used Nsight
to analyze my CUDA kernel program.\newline~
~\newline~
PB3:~ I tried to use python to write test code that contains native PyTorch LayerNorm and custom CUDA kernel
But some unknown and difficult errors really confused me, and I think all of those confusion and errors
couldn't be resolved in a short period.
